---
title: "Assignment 1 - Binomial Model"
author: "Valery Pugacheva"
date: "January 30, 2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE)
install.packages("derivmkts")
library(derivmkts)
```


This is the solution to exercises 4 of Assignment 1. Let's first define the parameters:
```{r}
S0 <- 40
K <- 40
r <- .04
sigma <- .3
time_T <- 1/2
div <- 0
```

This is the answer for *4 (a)*
```{r}
x <- binomopt(S0, K, sigma, r, time_T, div, nstep = 2, american=FALSE,
putopt=FALSE, specifyupdn=FALSE, crr=TRUE, jarrowrudd=FALSE,
returntrees=FALSE, returnparams=FALSE,
returngreeks=FALSE)

round(x, 5)
```

This is the answer for *4 (b)*
```{r}
x <- binomopt(S0, K, sigma, r, time_T, div, nstep = 10, american=FALSE,
putopt=FALSE, specifyupdn=FALSE, crr=TRUE, jarrowrudd=FALSE,
returntrees=FALSE, returnparams=FALSE,
returngreeks=FALSE)

round(x, 5)
```

This is the answer for *4 (c)*
```{r}
x <- binomopt(S0, K, sigma, r, time_T, div, nstep = 100, american=FALSE,
putopt=FALSE, specifyupdn=FALSE, crr=TRUE, jarrowrudd=FALSE,
returntrees=FALSE, returnparams=FALSE,
returngreeks=FALSE)

round(x, 5)
```

This is the answer for *4 (d)*
```{r}
x <- binomopt(S0, K, sigma, r, time_T, div, nstep = 10, american=TRUE,
putopt=FALSE, specifyupdn=FALSE, crr=TRUE, jarrowrudd=FALSE,
returntrees=FALSE, returnparams=FALSE,
returngreeks=FALSE)

round(x, 5)
```

This is the answer for *4 (e)*
```{r}
x <- binomopt(S0, K, sigma, r, time_T, div, nstep = 50, american=TRUE,
putopt=TRUE, specifyupdn=FALSE, crr=TRUE, jarrowrudd=FALSE,
returntrees=FALSE, returnparams=FALSE,
returngreeks=FALSE)

round(x, 5)
```

This is the answer for *4 (f)*
```{r}
x <- binomopt(S0, K, sigma, r, time_T, div, nstep = 10000, american=TRUE,
putopt=TRUE, specifyupdn=FALSE, crr=TRUE, jarrowrudd=FALSE,
returntrees=FALSE, returnparams=FALSE,
returngreeks=FALSE)

round(x, 8)
```

# Exercise 1: European Options

Let's first compute the limiting price of an European call/put (this is the celebrated Black-Scholes formula which you'll derive later in the course):
```{r}
d_1 <- (log(S0/K)+(r+sigma^2/2)*time_T) / (sigma*sqrt(time_T))
d_2 <- d_1 - sigma * sqrt(time_T)
bs_call_price <- S0*pnorm(d_1) - K*exp(-r*time_T)*pnorm(d_2)
bs_put_price <- K*exp(-r*time_T)*pnorm(-d_2) - S0*pnorm(-d_1)
bs_call_price
bs_put_price
```

